Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-28 article.qmd
Fix typos

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020];
Numba [@lamNumbaLLVMbasedPython2015], a Just-in-Time (JIT) compiler to LLVM;
SymPy [@meurerSymPySymbolicComputing2017], a library for symbolic mathematics;
and JAX [@jax2018github], a library that support automatic differentation
and compilation to GPUs and TPUs;
but it is easy to add new backends.

@@

Switching backends to `"numba"` can improve model runtime
on a factor upto x30 or more for big or long running models,
but incurs in a compile time penalty for the first run
which must be taken into account.

>>>>

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020];
Numba [@lamNumbaLLVMbasedPython2015], a Just-in-Time (JIT) compiler to LLVM;
SymPy [@meurerSymPySymbolicComputing2017], a library for symbolic mathematics;
and JAX [@jax2018github], a library that support automatic differentiation
and compilation to GPUs and TPUs;
but it is easy to add new backends.

@@

Switching backends to `"numba"` can improve model runtime
on a factor up to x30 or more for big or long running models,
but incurs in a compile time penalty for the first run
which must be taken into account.
